Helixer: Cross-species Gene Annotation Of Large Eucaryotic Genomes Using Deep Learning

### 2020-06-04 paper/main.tex
some polishing and author rearrangements

\title[short Title]{Helixer: Cross-species Gene Annotation Of Large Eucaryotic Genomes Using Deep Learning}
\author[Sample \textit{et~al}.]{Felix Stiehler\,$^{\text{\sfb 1,}}$$^\dagger$, Alisandra Denton\,$^{\text{\sfb 1,}}$$^\dagger$\, Marvin Steinborn\,$^{\text{\sfb 1}}$, Daniela Dey, Stephan Scholz, Andreas Weber\,$^{\text{\sfb 1,}*}$}
\address{$^{\text{\sf 1}}$Institue for Plant Biochemistry, Heinrich-Heine-University, Dusseldorf, D-40225, Germany}

\corresp{$^\dagger$Authors contributed equally. \newline $^\ast$To whom correspondence should be addressed.}

@@

\section*{Funding}
This work has been supported by the... \vspace*{-12pt}

\section*{Acknowledgements}
We are grateful for the computational suppport and GPU access provided by
the de.NBI cloud, and by both the Centre for Information and Media Technology (ZIM)
and the institute of Quantitative and Theoretical Biology at Heinrich Heine University.

>>>>

\title[short Title]{Helixer: Cross-species Gene Annotation Of Large Eucaryotic Genomes Using Deep Learning}
\author[Sample \textit{et~al}.]{Felix Stiehler\,$^{\text{\sfb 1}}$, Marvin Steinborn\,$^{\text{\sfb 1}}$, Stephan Scholz, Daniela Dey, Andreas P.M. Weber\,$^{\text{\sfb 1,}*}$, Alisandra K. Denton\,$^{\text{\sfb 1}}$}
\address{$^{\text{\sf 1}}$Institue for Plant Biochemistry, Heinrich-Heine-University, Dusseldorf, D-40225, Germany}

\corresp{$^\ast$To whom correspondence should be addressed.}

@@

\section*{Funding}
This work has been supported by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) 
under Germany's Excellence Strategy--EXC-2048/1--Project ID: 390686111.\vspace*{-12pt}

\section*{Acknowledgements}
We are grateful for the computational suppport and GPU access provided by
the de.NBI cloud, and by both the Centre for Information and Media Technology (ZIM)
and the Institute of Quantitative and Theoretical Biology at Heinrich Heine University.
